\ttlfnt{Comparing the performance of websites and their content distribution networks}

### 2016-08-28 Writeup/paper.tex
Update abstact conclusions

\begin{abstract}
Modern internet infrastructure consists of deep hierarchies of caches and Content Delivery Networks in order to serve the ever-increasing demand for high-bandwidth multimedia content. In this report we present a tool for measuring the impact of Content Delivery Networks on the performance of streaming video and audio content over the internet. We analyse the performance impact of these networks from the point of view both of the home user and large-scale institutions. We find that the majority of unpopular videos are not cached within South Africa. The video has to be obtained from a Google cache in Europe. We find that after viewing the unpopular video it is cached on both on the ISP's server and Google's South African cache. Subsequent views from the same ISP come from the ISP cache and views from another ISP come from Google's South African cache instead of from Europe. On the institutional network we find that even though, on the second view, an unpopular YouTube video is obtained from the institution's cache, the throughput is always slower than the third view.
\end{abstract}

>>>>

\begin{abstract}
Modern internet infrastructure consists of deep hierarchies of caches and Content Delivery Networks in order to serve the ever-increasing demand for high-bandwidth multimedia content. In this report we present a tool for measuring the impact of Content Delivery Networks on the performance of streaming video and audio content over the internet. We analyse the performance impact of these networks from the point of view both of the home user and large-scale institutions. We find that the less popular YouTube content is not cached in South Africa, instead needing to be retrieved from Europe. We also find that the performance increase from local YouTube caches improves across multiple retrievals instead of just one.
\end{abstract}
